A Lyapunov Analysis of Momentum Methods \\ in Optimization

### 2016-10-28 LyapDraft.tex
small change
Update LyapDraft.tex

The subequations corresponding to~\eqref{Eq:AlgoForward1} may be difficult to solve. For reference, the proximal minimization method~\cite{ChenTeboulle93}, 
\begin{equation}
x_{k+1} = \arg\min_{x\in\X} \left\{ f(x) + \frac{1}{A_{k+1} - A_k}D_h\left(x, x_k\right)\right\},
\end{equation}
involves applying the implicit-Euler method to the mirror descent dynamic, and both obtain a $O(1/A_k)$ convergence rate. Nevertheless, the proof structure which we demonstrated from this thought experiment serves as the backbone for analyzing many discretizations of \eqref{Eq:DynaBeta}, several of which constitute popular methods used throughout optimization.

@@

$\substack{\text{Frank-Wolfe}\\\text{ Algorithm }}$ & linear  & $f(x_k)$ & $ \frac{1}{2}\sum_{i=0}^{k}\frac {(A_{i+1} - A_i)^2}{A_{i+1}} diam(\X)^2$\\

>>>>

The subequations corresponding to~\eqref{Eq:AlgoForward1} may be difficult to solve. For reference, the proximal minimization method~\cite{ChenTeboulle93}, 
\begin{equation}
x_{k+1} = \arg\min_{x\in\X} \left\{ f(x) + \frac{1}{A_{k+1} - A_k}D_h\left(x, x_k\right)\right\},
\end{equation}
involves applying the implicit-Euler method to the mirror descent dynamic, and both yield a $O(1/A_k)$ convergence rate. 
%MJ This sentence isn't clear, and I'm not sure it's worth including.
%Nevertheless, the proof structure which we demonstrated from this thought experiment serves as the backbone for analyzing many discretizations of \eqref{Eq:DynaBeta}, several of which constitute popular methods used throughout optimization.

@@

$\substack{\text{Conditional Gradient}\\\text{ Method }}$ & linear  & $f(x_k)$ & $ \frac{1}{2}\sum_{i=0}^{k}\frac {(A_{i+1} - A_i)^2}{A_{i+1}} diam(\X)^2$\\
